Verifying Spatial Properties of Stencil Computations

### 2016-11-16 paper.tex
setion 2.1 edit
added paragraph to evaluation pointing out that inference mode is not the normal way to use the tool

We first examined how frequently stencil computations occur in our
corpus of Fortran code. This was carried out by running CamFort in
whole-code-base inference mode. We parsed 959,427 lines of Fortran
code and found that 10\% (97,439) of statements have a left-hand side
is an array subscript on neighbourhood indices. This supports the idea
that stencil-like computations are common in scientific code.

We would not expect to infer a stencil for each of these statements
because our stencil language places significant restrictions on the
types of array-subscript-statements that we will class as a
stencil. In fact, CamFort was able to infer a stencil from 30\% of
these statements. A single statement can produce multiple stencils and
we ended up with 60,525 stencils. This shows that we can still express
a large number of stencil uses within our high-level abstraction.

>>>>

We first examined how frequently stencil computations occur. We parsed
959,427 lines of Fortran code and found that 10\% (97,439) of
statements have a left-hand side is an array subscript on
neighbourhood indices. This supports the idea that stencil-like
computations are common in scientific code.

We used CamFort in inference mode to identify stencils within the
corpus. This assumes that the programs have been implemented
correctly---normally one would use CamFort in verification mode to
check the correctness of new code.

We would not expect to infer a stencil for each array statement we
found because our stencil language places significant restrictions on
the types of array-subscript-statements that we will class as a
stencil. In fact, CamFort was able to infer a stencil from 30\% of
these statements. A single statement can produce multiple stencils and
we ended up with 60,525 stencils. This shows that we can still express
a large number of stencil uses within our high-level abstraction.
